Predicting Internet Path Dynamics and Performance with Machine Learning

### 2017-12-20 paper-tex/paper.tex
Figure3.1 - Figure3.3 updated

	\begin{figure}[tp]
		\centering
		\begin{subfigure}[t]{0.4\linewidth}
			\centering
			\includegraphics[width=0.95\linewidth, trim={100 100 0 0}, clip=true]{fig/total_life_8}
			\label{fig:3.1a}
		\end{subfigure}
		\begin{subfigure}[t]{0.4\linewidth}
			\centering
			\includegraphics[width=0.95\linewidth, trim={100 100 0 0}, clip]{fig/total_life_20}
			\label{fig:3.1b}
		\end{subfigure}
		\begin{subfigure}[t]{0.4\linewidth}
			\centering
			\includegraphics[width=0.95\linewidth, trim={100 100 0 0}, clip=true]{fig/total_life_21}
			\label{fig:3.1c}
		\end{subfigure}
		\begin{subfigure}[t]{0.4\linewidth}
			\centering
			\includegraphics[width=0.95\linewidth, trim={100 100 0 0}, clip]{fig/total_life_30}
			\label{fig:3.1d}
		\end{subfigure}
		\caption{Temporal patterns of route life among 4 different paths.}
		\label{fig:3.1}
	\end{figure}

	\begin{figure}[!htp]
		\centering
		\begin{subfigure}[t]{0.4\linewidth}
			\centering
			\includegraphics[width=0.95\linewidth, trim={100 100 0 0}, clip=true]{fig/route_change_8}
			\label{fig:3.2a}
		\end{subfigure}
		\begin{subfigure}[t]{0.4\linewidth}
			\centering
			\includegraphics[width=0.95\linewidth, trim={100 100 0 0}, clip]{fig/route_change_20}
			\label{fig:3.2b}
		\end{subfigure}
		\begin{subfigure}[t]{0.4\linewidth}
			\centering
			\includegraphics[width=0.95\linewidth, trim={100 100 0 0}, clip=true]{fig/route_change_21}
			\label{fig:3.2c}
		\end{subfigure}
		\begin{subfigure}[t]{0.4\linewidth}
			\centering
			\includegraphics[width=0.95\linewidth, trim={100 100 0 0}, clip]{fig/route_change_30}
			\label{fig:3.2d}
		\end{subfigure}
		\caption{Temporal patterns of the number of route changes among 4 different paths.}
		\label{fig:3.2}
	\end{figure}

	\begin{figure}[!htp]
		\centering
		\begin{subfigure}[t]{0.4\linewidth}
			\centering
			\includegraphics[width=0.95\linewidth, trim={100 100 0 0}, clip=true]{fig/RTT_8}
			\label{fig:3.3a}
		\end{subfigure}
		\begin{subfigure}[t]{0.4\linewidth}
			\centering
			\includegraphics[width=0.95\linewidth, trim={100 100 0 0}, clip]{fig/RTT_20}
			\label{fig:3.3b}
		\end{subfigure}
		\begin{subfigure}[t]{0.4\linewidth}
			\centering
			\includegraphics[width=0.95\linewidth, trim={100 100 0 0}, clip=true]{fig/RTT_21}
			\label{fig:3.3c}
		\end{subfigure}
		\begin{subfigure}[t]{0.4\linewidth}
			\centering
			\includegraphics[width=0.95\linewidth, trim={100 100 0 0}, clip]{fig/RTT_30}
			\label{fig:3.3d}
		\end{subfigure}
		\caption{Temporal patterns of round trip time among 4 different paths.}
		\label{fig:3.3}
	\end{figure}

>>>>

	\begin{figure}[tp]
		\centering
		\begin{subfigure}[t]{0.45\linewidth}
			\centering
			\includegraphics[width=0.95\linewidth]{fig/total_life_8}
			\label{fig:3.1a}
		\end{subfigure}
		\begin{subfigure}[t]{0.45\linewidth}
			\centering
			\includegraphics[width=0.95\linewidth]{fig/total_life_20}
			\label{fig:3.1b}
		\end{subfigure}
		\begin{subfigure}[t]{0.45\linewidth}
			\centering
			\includegraphics[width=0.95\linewidth]{fig/total_life_21}
			\label{fig:3.1c}
		\end{subfigure}
		\begin{subfigure}[t]{0.45\linewidth}
			\centering
			\includegraphics[width=0.95\linewidth]{fig/total_life_30}
			\label{fig:3.1d}
		\end{subfigure}
		\caption{Temporal patterns of route life among 4 different paths.}
		\label{fig:3.1}
	\end{figure}

	\begin{figure}[!htp]
		\centering
		\begin{subfigure}[t]{0.45\linewidth}
			\centering
			\includegraphics[width=0.95\linewidth]{fig/route_change_8}
			\label{fig:3.2a}
		\end{subfigure}
		\begin{subfigure}[t]{0.45\linewidth}
			\centering
			\includegraphics[width=0.95\linewidth]{fig/route_change_20}
			\label{fig:3.2b}
		\end{subfigure}
		\begin{subfigure}[t]{0.45\linewidth}
			\centering
			\includegraphics[width=0.95\linewidth]{fig/route_change_21}
			\label{fig:3.2c}
		\end{subfigure}
		\begin{subfigure}[t]{0.45\linewidth}
			\centering
			\includegraphics[width=0.95\linewidth]{fig/route_change_30}
			\label{fig:3.2d}
		\end{subfigure}
		\caption{Temporal patterns of the number of route changes among 4 different paths.}
		\label{fig:3.2}
	\end{figure}

	\begin{figure}[!htp]
		\centering
		\begin{subfigure}[t]{0.45\linewidth}
			\centering
			\includegraphics[width=0.95\linewidth]{fig/RTT_8}
			\label{fig:3.3a}
		\end{subfigure}
		\begin{subfigure}[t]{0.45\linewidth}
			\centering
			\includegraphics[width=0.95\linewidth]{fig/RTT_20}
			\label{fig:3.3b}
		\end{subfigure}
		\begin{subfigure}[t]{0.45\linewidth}
			\centering
			\includegraphics[width=0.95\linewidth]{fig/RTT_21}
			\label{fig:3.3c}
		\end{subfigure}
		\begin{subfigure}[t]{0.45\linewidth}
			\centering
			\includegraphics[width=0.95\linewidth]{fig/RTT_30}
			\label{fig:3.3d}
		\end{subfigure}
		\caption{Temporal patterns of round trip time among 4 different paths.}
		\label{fig:3.3}
	\end{figure}
